How to Find GENERAL Defect Prediction Models \\ Amidst Hundreds of Software Projects

### 2020-03-12 response.tex

\response{ Thank you very much for your encouraging comments. We have made appropriate changes to the manuscript taking into careful consideration the recommendations of the reviewers. We hope that this new draft adequately satisfies all the issues raised by the reviewers. To assist the reviewers in tracking all the new changes, where appropriate, we have prefixed the text with \respto{X-XX} to correspond to the reviewers' questions.~\\
Below is the brief summary of our changes:
\be
\item The problem statement has been  clarified and properly positioned (R1, R3).
\item The novelty of the approach has  been clarified (R3). (see \bareresp{3-1})
\item Using comments from  (R1, R2, R3), we have made numerous small editorial improvements.
\item The study now includes all the details to ensure replicability (R1, R2).
\item The results of the study need to be revisited since the reviewers are not convinced that the results support the claims in the paper (R1, R2, R3).
\item The background on transfer learning has been augmented with more  citations (R2).
\ee}

\section*{Reviewer 1}

\response{Thank you very much for your detailed review. We have made some additional corrections, clarifications, and revisions, as directed by your comments. To assist in your review, we refer to specific locations of each of the changes using \respto{1-XX}.}

\review{(1.1a) Background. The paper builds upon a number of previous studies. However, several key questions have no answer: *What is* the bellwether? *Why is* this relevant? How does it work when applied to different contexts? Why is this useful in practice?}

\response{(1.1b)You are quite correct, we did not define bellwether till very late in the prior draft. In this draft, we define bellwether on page 1\respto{1-1a}}

@@

\review{The paper mentions that: "The core intuition of this new approach is that if many projects are similar, then we do not need to run comparisons between all pairs of projects": very good, but where this intuition come from?}

\response{Thank you for that comment.  You a re quite correct-- we did not document the source of our intutuion. We have added the following note to \respto{1-1b}}

\begin{quote}
\response{``The core intuition of this new approach is two-fold. Firstly,
many projects are similar in structure. We say this since  Devanbu
et al.`\cite{hindle2012naturalness}   report that if Markov chains are created for tokens in a program,
then a remarkably small number of chains capture most of the program. ~\\
``Secondly, given these similarities,   we can exploit symmetries between different projects in order to learn predictors from one and apply those to another. To say that another way, given large scale similarities between projects,  then we do not need to run comparisons between all pairs of projects since analyzing just a few pairs should work as well as anything else.''}
\end{quote}

@@

\review{(1.2)The relevance of the paper. This is, unfortunately, unclear. According to the abstract and introduction, the main issue treated in the paper is related to scalability. Please, provide a clear case study on the performance of bellwether methods. The claims on the scalability of the approaches are just claims, no details are reported. Abstract and introduction just report that "when applied to the 697 projects studied here, they took 60 days of CPU to find and certify the bellwether". As said, the bellwether approach has been applied to several problems (e.g., defect prediction/effort estimation/bad smell detection): are these problems the same? When is it needed to apply scalable solutions for bellwether approaches? Why? Please, explain.}

\response{ need a new RQ0: how slow is standard bellwether. theoretically an empirically its slow (chart on p2. move to RQ0). May need to include results using increasing community size.XXX including an comparison study with varying size of community to start with. Still need to write this}

\review{(1.3a) Writing style. The introduction is, simply, to be completely rewritten}

\response{Thank you for your comment. On review, we found that core problem of conclusion instability
was not well documented in the introduction. This new draft fixes that problem. Much of the new
text on page1 takes care to document {\em why }
we are exploring conclusion instability before
moving on the {\em how} we do that exploration.}

\review{(1.3a)I would like to see a paper that is understandable even from non-experts. As such, please define the context of the paper, the concepts of (1) software quality - line 1, (2) general models - line 2, (3) many projects - line 2, (4) "scalable approach to learning effective models adapted to the task at hand" - line 2/3, (5) "or does the truth lie somewhere in-between" - line 3. These are just of the examples of why the introduction is unclear and does not provide any detail on the reasons behind the paper. The same is true for the remaining of the paper, which gives for granted many of the concepts without explaining them properly.}

\response{Thank you for your comment. We have rewritten the introduction to be more understandable from a non-expert view and added necessary definitions where required.}

@@

\review{(1.4) Please, avoid claims such as "have tremendous practical significance" without providing any practical significant example/citation. (This is just an example)}

\response{ Thank you for your comment, you are right.In this manuscript we have deleted the  superlatives (including that one)}

@@

\review{(1.5a) The clarity and replicability of the paper are unclear. Here some examples 1) "The logistic regression learner (since it is relatively fast)". What does "fast" mean? How was "fast" computed? }

\response{ Thank you for your comment, you are quite right. We had not properly mentioned the reason behind choosing logistics regression. In this draft we have added the reasons to \respto{1-5a}:}

\begin{quote}
\response{
"The logistic regression learner,  since it is widely used in defect prediction~\cite{ghotra2015revisiting,XXX} in software engineering domain and it is relatively fast in terms of model building time than other learners such as Support Vector Machine, Random Forest, Artificial Neural Nets etc. tested on defect prediction.~\cite{ghotra2015revisiting}}
\end{quote}

@@

\review{(1.5b)
2) "The SMOTE class imbalance correction algorithm [49], which we run on the training data2". Why is SMOTE needed? Why is the problem unbalanced? Please, explain.
}

\response{You are right, we had not included the reason for using SMOTE in our algorithm and had not explained why the problem is unbalanced. In this draft we have added notes to answer those questions \respto{1-5b}:}
\begin{quote}
    \response{The SMOTE class imbalance correction algorithm~\cite{Chawla2002}, since many of the projects have relatively very few or large number of defects. A model build on project with such skewed class distribution can result in a biased model towards the majority class (Such models can either have low recall or high recall with high pf). Thus we run SMOTE on the training data to artificially boost the number of target examples in the training data and achieving balanced recall and pf for the minority class test examples}
\end{quote}

@@

\review{(1.5c)
3) "and Hall’s CFS feature selector". Which features have been removed and why?
}

\response{You are quite correct, we did not included the details about how the features are being removed and why in the last draft. In this draft we have included notes regarding how CFS works and why the features that are not used are removed \respto{1-5b}:}

\begin{quote}
    \response{Hall's CFS feature selector~\cite{hall1999correlation} is used to identify features which are highly correlated with the classification, yet uncorrelated to each other. The features which are  highly correlated with each other will not add more information while making classification, while the features which are uncorrelated towards the classification also not add more information while making classification. The CFS algorithm incrementally picks one feature at a time which adds the most information towards the classification at a given step and stops when there is no more improvement in the score.}
\end{quote}

@@

\review{(1.5d)
4) "As to CFS, we found that without it, our recalls were very low and we could not identify which metrics mattered the most". Where can the reader understand this statement? Where is the replication data? }

\response{Thank you for your comment, using the replication package (including data) the experiments can be reproduced.\respto{1-5h}}

@@

\review{(1.5e)
5) "extensive studies have found that CFS more useful than many other feature subset selection methods such as PCA or InfoGain or RELIEF". The paper cites just one paper, how should these studies be "extensive"? }

\response{Thank you for that comment.  You are quite correct-- we did not document the all the necessary citations for supporting our claim before. We have added the following note to \respto{1-5e}}

\review{(1.5f)
5) "Maximize recall and precision and popt(20)": Why should these metrics be maximized? What is the practical value, e.g., is high recall always needed in practice, or should we prefer precision in the problems treated by the bellwether? What about popt(20)?}

\response{Thank you for your comment, we didn't explained why these metrics need to be maximized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}

@@

\review{(1.5g) "While minimizing false alarms and ifa auc": Again, please explain the practical relevance of the performance metrics employed. }

\response{Thank you for your comment, we didn't explained why these metrics need to be minimized, added necessary details\respto{1-5f} as footnote also there are details in sec 4.5}

@@

\review{(1.5h) 
More in general, how can one replicate the performed study? Is there a replication package? If so, where?}

\response{Thank you for that comment. You are quite correct-- we did not include in depth steps to replicate the study before. We have added a replication package in contribution section \respto{1-5h} as well as more in depth details about the algorithm has been added in \respto{XXXX}}

\review{(1.6a) The analysis of the results should be substantially improved. Let consider the case of Section 5 - RQ1. The results are reported in less than half column and refer to a figure (Figure 6) which does not explain anything. The summary reports that "Theoretically and empirically, the hierarchical reasoning on GENERAL performs much faster than standard bellwether methods": I cannot understand where these "theoretically and empirically" come from, since there is no proof of them. }

\response{you are right, in the last draft we indeed did not included detailed analysis of the results to show the scalability of our model. In this draft \respto{1-2}\respto{1-6a} we have included 2 more research questions (RQ1 and RQ2) to show the conventional bellwether is slower than the new bellwether (aka GENERAL) method. We also have updated another research question (RQ3) to compare the methods in-term of number of comparisons and time taken to run the two methods, as can been seen in figure~\ref{fig:compare} and \ref{fig:compare_time}.}

\review{(1.6b)
The same is true for the other research questions. And, in general, there is qualitative analysis: Why are the results the ones reported in the paper?}

\response{you are right,Thank you for that comments. We have added much  quantitative analysis as
well as statistical tests to this paper. Please see figure~\ref{fig:compare} and \ref{fig:compare_time}. XXXX(do we need more analytics and if so what?)}

@@

\review{(1.6c) What makes the reported method scalable?}

\response{Thank you for your comment, in this version we have updated the RQ3 to show that our method is scalable. We have showcased the analysis of number of comparisons and run time between the two algorithm (conventional bellwether and GENERAL) using various community size.}

\section*{Reviewer}

Many of your comments take issue with two terms used in this paper "lessons learned" and "transfer learning".
We agree with you that our use of "lessons learned" was inappropriate and we have removed all those usages.

As to our use of "transfer learning", 
inspired by your comments we have clarified what we mean by that term much earlier in the paper (see \cite{XXX}). Base don that clarification, we can show that our use of ``transfer learning'' is consistent with its usage by Pan'09 (a paper current 8,220 citations at the time of this writing). Also, our usage is consistent with dozens of recent SE research papers on transfer learning~\cite{XXXmanycite}. Thank you for encouraging us to clarify that terminology.

@@

% \review{These lessons learned are reviewed when new projects are being initiated/planned. The introduction talks about guiding project management but project management has a process for handling lessons learned that doesn’t require machine learning. How does the method help that process? Why would you need a “bellwether” to apply lessons learned to a new project?! The method does not transfer lessons learned but what it DOES appear to do is associate defect rate profiles for two projects (a so-called “bellwether” and a new project).}

% \response{ ur rught we renamed as you said. }

\review{(2.2) [Sec. 1] “…the bellwether is equivalent to the other models…” This claim is confusing. 1) Is “the bellwether” a model or a project? 2) How is equivalence defined? Or do you simply mean “similar”?}

\response{ Thank you for your comment, in the last draft we did not accurately explain what bellwether is. In this draft we have included the definition of bellwether \respto{1-1}\respto{2-2}:}

\begin{quote}
    \response{``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others. Also, to answer your second question, ``…the bellwether is equivalent to the other models'' has been replaced with ``....since the bellwether is an exemplar projects for the community of N projects seen so far...''  }
\end{quote}

@@

\review{(2.3) [Sec. 1] “when new projects appear, their quality can be evaluated even before there is an extensive experience base within that particular project (again, just by studying the bellwether).” You take a set of projects…select one project (the “bellwether”)…then use that project to build a model that can—for instance—estimate defect rate. So, for the defect estimation case, the model learned from the bellwether won’t tell you where the defects may be (i.e., fault localization), it will just estimate how buggy a new project is. Is all of this right?}

\response{Thank you for your comment. In the first draft we did not adequately explained the goal of the task we are exploring. In this version we have added proper details regarding the task, that is to explore defect prediction to localize bugs in project's codebase  using software quality metrics extracted from the projects and the details has been added at \respto{2-3}.}

@@

\review{(2.4) If the point is to use the bellwether to infer things about a “new” project, then how new can the new project be? When (in the new project’s history) can you be sure the model from the bellwether is valid to use?}

\response{Explain the train, test splits and the how you do the exp. then say this is what our model proves, it predicts for projects which it has not seen before XX.}

\review{(2.5) Do you have to find a bellwether for each purpose? In other words, if you find a bellwether among 697 projects for defect rate prediction, then is that same bellwether automatically used to build a model for another discrete task (different than defect rate prediction)? Or will you have to apply this algorithm for each and every discrete task?}

\response{Thank you for your comment, it was unclear in the previous manuscript whether we need to find different bellwether for discrete task (different than defect rate prediction). For finding bellwether for another task, different from defect prediction, we do need to find another bellwether. The reason being, for other tasks the model build using the data will be different, so similarity between models  built using the projects will also be different.}

@@

\review{(2.6) Figure 1 needs to be omitted}

\response{You are correct, it is certainly confusing for intro. we have removed the hypothetical figure and texts associated with it.}

@@

\review{(2.8) The paper does not evaluate the model’s performance using a pool of 12,000 projects; the evaluation does not even use 1,000 projects.}

\response{will fix}

\review{(2.9) [Sec. 1] The box under RQ4 is very confusing. We find the bellwether to simply study one project, but this note says we still need to analyze hundreds of projects to understand something like the importance of features. Is this right?}

\response{You are correct, the wording of the box under RQ4 was confusing. We have added new texts \respto{2-9} to be more clear about the  context about finding bellwether to understand importance of features. To be more precise, instead of finding important features for each project (which shows very different results for each project), we find the bellwether (as an exemplary project for all other projects) using GENERAL and check the importance of feature for that project only.}

@@

% \response{(2.10d) 
% [B] Steps 2 and 3 involve grouping the projects based on similarity. There is no transfer learning here.}

% \response{(2.10e) 
% [C] There is no transfer learning done in Steps 4-6.}

% \response{(2.10f) 
% [D] Aside from inspecting each step in the main procedure, another way to determine whether GENERAL involves transfer learning is the following: This approach does not involve reweighting instances nor does it appear to involve transferring feature representations and/or parameters…and if it does then the paper does not even identify this fact much less argue for it being the case.
% If something in this rationale [A-D] is not correct, then please clear up the explanation on transfer learning in the paper in terms/language the machine learning community has established to avoid ambiguity.}

\review{(2.10) I do not understand what the second contribution really is.}

\response{
Thank you for that comment. Yes you are completely correct.
 On  review,  we  found that  core  problem  of  conclusion  instability  was  not  well documented  in  the  introduction.  This  new  draft  fixes  that problem. Much of the new text on page1 takes care to document {\em why } we  are  exploring  general SE conclusions  before moving on the
 {\em how} we do that exploration.}

 \response{
Note that with that new introduction (that focuses more on {\em why}, then this paper is not  better at contextualizing
and justifying the need (and value) of the second contribution.}

% yes, we have deleted it. But this is one of the main points, can we answer not it}

@@

\review{(2.11) [Sec. 2.1] I recommend removing this subsection from Background and condensing it in the motivation in Sec. 1.}

\response{Yes! Good idea. We have done that.}

\review{(2.12) [Sec 2.2] Figure 2 needs to be omitted. These “hypothetical” plots are not substantial. (The authors even say as much when discussing the results in Sec. 5.)}

\response{Thank you for your comments, we have moved [Sec. 2.1] from background to a new section titled Motivation. Also we have removed the hypothetical situation and added actual experimental data to show the difference. The details has been added as text in \respto{2-12}.}

\review{(2.13) [Sec. 2.2] At least two-thirds of this sub-section is anecdotal. Does the gist of this subsection depend critically on the hypothetical?}

\response{Thank you for your comments, we have removed the hypothetical graph and added experimental details for this section. The new text has been added to [Sec. 2.2], which is a part of motivation now \respto{2-12}.}

@@

\review{(2.14) [Sec. 2.3] “Accordingly, here, we explore nearly 700 projects.” But just because 697 (this study) is larger than 24 (previous studies) does not mean external validity concerns are adequately addressed when one considers how complex the task is. Please comment.}

\response{with respect, in terms of SE research, it is much larger than any studies seen before. but your concern is valid. we have added
a weaselt sentence at the end saying that we can never assume generality of all porkect.XXX}

\review{(2.15) [Sec. 2.3] “If they ask ‘are we sure XYZ causes problems?’, can we say that we have mined enough projects to ensure that XYZ is problematic?” We can say XYZ is probably problematic, but that doesn’t answer the deeper question about causality. Do you agree?}

\response{ You are quite right. we should never say "cause'. We have removed the ambiguous statement and added XYZ is a statistical predictor for bug prone code. The changes has been added in this manuscript\respto{2-15} }

@@

% \review{(1.16) [Sec. 2.4] “This art of moving data and/or lessons learned from one project to another is Transfer Learning.” I do not agree with this definition. Please cite this definition or use the definition of transfer learning established by the machine learning community.}

\review{(2.17) [Sec. 2.4] “Successful transfer learning can have two variants…” Cite these variants. This is a software engineering paper—not a machine learning paper—that should reference other work for these fundamental details.}

\response{Thank you for your comment. We indeed forgot to add the citations in the previous manuscript. We have added the citations in this manuscript \respto{2-17}.}

@@

\review{(2.18) [Sec. 3.2] “…for large sample datasets…” What is the size of the design matrix? Does 21 product metrics and five process metrics mean 26 columns? If there are 697 projects and snapshots every six months, then how many rows are there?}

\response{XXX}

\review{(2.19) [Sec. 3.3] “As discussed below, the defect models assessed in these experiments” Incomplete.}

\response{Thank you for your comment, we have fixed the incomplete sentence.}

\review{(2.20) [Sec. 4.1] “stratified k=5 fold cross-validation an” Incomplete.}

\response{Thank you for your comment, we have fixed the incomplete sentence. We have also ensured there are no more incomplete sentences in this version.}

\review{(2.21) [Sec. 5] “To put that another way, the answer to ‘is is [sic] possible to learn from too much data’, is ‘depends on what you value’” How does your concept of learning from too much data relate to the concept of overfitting? Same concept? Different concepts? If so, how are they different?}

### 2020-03-12 manuscript.tex
Updates from Overleaf

But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For example, for nearly 700 projects,
the defect prediction models generated from GENERAL's bellwether  
were  just as good as those found via  standard methods.

@@

%   After a decade of intensive research into automated software analytics, what general principles have we learned? While that work has generated specific results about specific projects~\cite{Bird:2015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).

@@

\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
\bi
\item Predicting if a submitted code is likely to buggy or not.
\item Improving code quality by detecting code smells.
\item Issue lifetime estimation to enable effective development and maintenance of their software systems.
\ei

Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them. With large quantity of data available to them, how should they reason about software quality? Should they use  general models that hold over many projects? Or must they use an ever-changing set of ideas that are   continually adapted to the task at hand? If the latter were true then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
%One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis. A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}). Such small samples can never represent something as diverse as software engineering.

Finding general lessons across multiple projects is a complex task.
A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}. \respto{1-1}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).  This method:
\bi
\item Finds a  ``bellwether'' project that is exemplar for the rest;
\item Draw conclusions from  that project.
\ei
This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization. As a method of transferring lessons learned from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}.

%In terms of {\em transfer} and {\em lessons learned},  such bellwethers have
 % tremendous practical significance. 
  When new projects arrive, then even before there is much experience with those new projects,  lessons learned from other projects can be applied to the new project (just by studying the bellwether),
 Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
 %since the bellwether is similar to the other models
 then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

@@

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects can be better than learning just from your own local project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods. For example: This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects. GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
% \bi
% \item
% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

@@

            \begin{RQ}{
               Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects. In this experiment the conventional bellwether method used almost 72 hours to find the ``bellwether''.}
            \end{RQ}

@@

            \begin{RQ}{
               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method took around 1.5 hours find a ``bellwether''.}
            \end{RQ}

@@

            \begin{RQ}{
                The importance of many key features is not apparent at the local
level. To fully appreciate the critical impact on defects
of class interface design,  it is necessary to conduct
a global analysis across hundreds of projects. }
            \end{RQ}

@@

\subsection{Why Seek Generality?}
\label{sec:Motivation}
There are many reasons to seek stable general conclusions in software engineering. If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.

\textbf{Generality:} Data science for software engineering cannot be called a ``science'' unless it makes general conclusions that hold across  multiple  projects. If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.

\textbf{Trust:} Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.

\textbf{Insight:} Kim et al.~\cite{Kim2016}, say  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. For Tan et al.~\cite{tan2016defining}, such   insights  are a core deliverable. Sawyer et al. agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Bird, Zimmermann, et al.~\cite{Bird:2015} say that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.

\textbf{Training:} Another concern is what do we train novice software engineers or newcomers to a project? If our models are not stable, then it hard to teach what factors  most influence software quality.

\textbf{Tool development:} Further to the last point--- if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.

@@

\subsection{Why Shun Generality?}
Just to balance the above argument,
we add that   sometimes it is possible to learn from {\em too much data}.
Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters. That is, they would predict that one model  will \underline{not}  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply. Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.

>>>>

But  existing  methods  for  bellwether  transfer  are  very slow.  When  applied  to  the  697  projects  studied  here,  they took  60  days  of  CPU  to  find  and  certify  the  bellwethers
Hence,  we  propose GENERAL:  a novel bellwether detection algorithm based on
  hierarchical clustering. At each level within a tree of clusters, one bellwether is computed from sibling projects, then promoted up the tree. 
This hierarchical method is a scalable approach to learning effective models from very
large data sets. 
For nearly 700 projects,
the defect prediction models generated from GENERAL's bellwether  
were  just as good as those found via  standard methods.

@@

\respto{1-3}{\color{blue}Researchers and industry practitioners makes use of data-driven decision making for defect prediction by generating software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics (such as number of revisions, lines added and deleted) These defect predictors are used for predicting defects in new set of changes and to learn what are the important metrics that are responsible for finding these defects. These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and can be used for large scale data-driven decision making.}

{\color{blue} But what is the external validity of the conclusions reached  via
the above data mining methods?
 If we cannot offer general rules across a large number of software projects, then it is   difficult to demonstrate such generality.
 Hassan~\cite{Hassan17} cautions that managers lose faith in software analytics if its models keep changing since  the assumptions used to make prior policy decisions may no longer hold.
Also, Kim et al.~\cite{Kim2016}, notes  that the aim of software analytics is to obtain actionable insights that help practitioners accomplish software development goals. Many other researchers agree. For example,
Tan et al.~\cite{tan2016defining} say that such   insights  are a core deliverable. Sawyer et al. agree, saying that  insights are the key driver for businesses to invest in data analytics initiatives~\cite{sawyer2013bi}. Also,
Bird, Zimmermann, et al.~\cite{Bird:2015} argue that such  insights occur when users reflect, and react, to the output of a model generated via software analytics. But if  new models keep being generated in new projects, then that exhausts the ability of  users to draw insight from  new data.}

{\color{blue} Apart from the above,  are several other reasons to seek general conclusions in SE. For example, 
if we are unsure what factors most influence quality, it is difficult to design and implement and deploy tools that can successfully improve that quality.
Also,
consider the task of training a   novice software engineers or newcomers to a project If our models are not stable, then it hard to teach what factors  most influence software quality.}

%Many Large organizations and many open source communities are using large scale data analysis on historical data available to them. With large quantity of data available to them, how should they reason about software quality? Should they use general defect prediction models that hold over many projects? Or must they use an ever-changing set of defect prediction models that are continually build and adapted to the task at hand? If the latter were true then there would be no stable models and conclusions about what is best practice for SE for avoiding defects (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability has detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}

% Researchers and industry practitioners makes use of different machine learning models to automatically generate software quality models(defect predictor) from project data comprises of software quality metrics (Commonly used software metrics for defect prediction are complexity metrics (such as lines of code, Halstead metrics, McCabe’s cyclometic complexity, and CK metrics) and process metrics(such as Number of revisions, lines added and deleted)) . Researches and industry practitioners use these defect predictors to predict for defect in new set of changes and to learn what are the important metrics that are responsible for finding these defects. These quality metrics can be collected with much ease from the code base of different software systems from large organizations and open source community, and

%   After a decade of intensive research into automated software analytics, what general principles have we learned? While that work has generated specific results about specific projects~\cite{Bird:-24015,menzies2013software}, it has failed (so far) to deliver general principles that are demonstrably useful across many projects~\cite{menzies2013guest} (for an example of how {\em more} data can lead to {\em less} general conclusions, see below in {\S}2a).

@@

% \respto{1-3}{\color{blue}Researchers and industry practitioners makes use of software analytics for many tasks to access software quality, such as:
% \bi
% \item Predicting if a submitted code is likely to buggy or not.
% \item Improving code quality by detecting code smells.
% \item Issue lifetime estimation to enable effective development and maintenance of their software systems.
% \ei

% Large organizations and many open source communities uses data-driven decision making, where they learn using large scale data analysis on historical data available to them. With large quantity of data available to them, how should they reason about software quality? Should they use  general models that hold over many projects? Or must they use an ever-changing set of ideas that are   continually adapted to the task at hand? If the latter were true then there would be no stable conclusions about what is best practice for SE   (since those best practices would keep changing as we move from project to project). As discussed in section~\ref{sec:Motivation}, such conclusion instability has   detrimental implications for {\em generality, trust, insight, training}, and {\em tool development}.}
%One  explanation for the limited conclusions (so far) from automated analytics is  {\em how much} data we are using for analysis. A typical software analytics research paper uses less than a few dozen projects  (exceptions: see~\cite{krishna18a, zhao17, agrawal18}). Such small samples can never represent something as diverse as software engineering.

{\color{blue} Finding general defect prediction models  across multiple projects is a complex task.
There are many recent examples of supposed ``general'' SE conclusions that are
now questionable. For example, Fenton warns
that, in stark contrast to  much prior research, pre- and post- release failures are not connected~\cite{fenton2000quantitative}.
Also, Nagappan et al. have found that the language construct GOTO, as used in contemporary practice, is rarely considered harmful~\cite{nagappan2015empirical};
Similiary, Fucci et al. report that test-driven development is not any better than "test last"~\cite{fucci2017dissection};
 Further, in our own work, we have seen that
 delayed issues are not exponentially more expensive to fix~\cite{menzies2017delayed}.
 For a long list of other conclusions that were found to be  unstable across multiple projects, see~\cite{Me13}. This problem is so endemic in software engineering that other journals have devoted entire special issues t the topic~\cite{Menzies2012}. }

{\color{blue} Given all these examples of SE conclusions whose generality we must now question, it is timely
to ask what methods are available for finding general results that hold across multiple projects?}
A new approach, that shows much promise, is the ``bellwether'' method for transferring conclusions between projects~\cite{krishna2018bellwethers,krishna16a,mensah18z,mensah2017stratification,mensah2017investigating}. \respto{1-1a}{\color{blue} ``bellwether'' is a project from a community of N projects, whose data yields the best analytic (i.e. defect prediction, effort estimation etc) on all others.} (the bellwether is the  leading sheep of a flock, with a bell on its neck).  This method:
\bi
\item Finds a  ``bellwether'' project that is exemplar for the rest;
\item Draw conclusions from  that project.
\ei
\respto{3-5}{\color{blue}This approach has been successfully applied to defect prediction, software effort estimation, bad smell detection, issue lifetime estimation, and configuration optimization (In this paper we only explore defect prediction). As a method of transfer learning from one project to another, bellwethers have worked better than the Burak filter~\cite{turhan09}, Ma et al.~\cite{Ma2012}'s transfer naive Bayes (TNB); and Nam et al.  TCA  and TCA+, algorithms~\cite{Nam13,Nam2015}}.

When new projects arrive, then even before there is much experience with those new projects,  models learned from other projects can be applied to the new project (just by studying the bellwether),
 Further, \respto{2-2}{\color{blue} since the bellwether is an exemplar projects for the community of N projects seen so far},
 %since the bellwether is similar to the other models
 then when new projects appear, \respto{2-3}{\color{blue} bugs can be localized for that project} even before there is an extensive experience base within that particular project (again, just by studying the bellwether).
 %That is, bellwethers can be queried  to find general lessons about (a)~major quality issues;
 %or (b)~best practices to avoid quality problems;
 %or (c)~cost-benefit justifications for buying or building tools can be made stable across a large number 
 %of projects.

@@

 This paper evaluates the model built from the project   found by GENERAL. 
 We will find that  the predictions
 from this model  are as good, or better,
 than those found  via ``within'' learning (where models are trained and tested on local data)
 or ``all-pairs'' learning (where models are found after building models from all pairs of projects).
   That is
\begin{quote}
{\em 
Learning from many other projects can be better than learning just from your own local project data.
}\end{quote}
GENERAL's clustering methods divide $N$ projects into $m$ groups. In that space,   GENERAL only needs
to compare $O(m*(N/m)^2)$  projects to find the bellwether. Theoretically and empirically, 
this means GENERAL will scale up much better than traditional   methods. This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects. GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).
% \bi
% \item
% This paper applies GENERAL and traditional $O(N^2)$ bellwether to 697 projects.
% GENERAL and the traditional approach terminated in 1.5 and 72 hours (respectively).

@@

            \begin{RQ}{
               Conventional bellwether method as proposed by krishna et al~\cite{krishna2018bellwethers,krishna16a} uses a $ O(N^2) $ comparisons to find the ``bellwether'' among a community of N (697 projects in this experiment) projects. In this experiment the conventional bellwether method is very expensive to find the ``bellwether''.}
            \end{RQ}

@@

            \begin{RQ}{
               The new bellwether method (GENERAL), which is a combination of hierarchical clustering and bellwether method achieves  a computational complexity of $O(m*(N/m)^2)$, which is much faster than conventional bellwether.}
            \end{RQ}

@@

            \begin{RQ}{
                \respto{2-9}\respto{3-13} {\color{blue}The importance of many key features is not apparent at the local
project level. To fully understand the effect of certain attributes (key features) on defect prediction and bug localization, it is necessary to analyze hundreds of projects together to identify a single bellwether. This bellwether will act as an exemplary model to identify such key features in defect prediction models.}}
            \end{RQ}

@@

%If our conclusions about best practices for SE projects keep changing, that will be detrimental to generality, trust, insight, training, and tool development.

@@

\subsection{A Note on Context}
%Just to balance the above argument,
%we add that   sometimes it is possible to learn from {\em too much data}.
Petersen and Wohlin~\cite{Petersen2009} argue that for empirical SE, context matters. That is, they would predict that one model  will \underline{not}  cover all  projects and that tools that report  generality  over many software projects need to also know the {\em communities} within which those conclusions   apply. Hence, this work divides into (a)~automated methods for finding sets of projects in the same {\em community}; and (b)~within each {\em community}, find the model that works best.
